Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain capitalize_subject

\subsubsection{capitalize_subject}
\label{subs:capitalize_subject}

>>>>

\subsubsection{capitalize_subject}
\label{subs:capitalize_subject}
The first letter of the subject line should be capitalized. Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the english language start with a capital letter. This rule is only mentioned by \cite{CB}. It may not be as important as other rules, but fullfilling it requires little effort and makes reading the message a nicer.
